Appendix to "Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2023-07-24 src/docs_paper/appendix.Rmd
Update paper and appendix #55

ks_summary %>%
  ungroup() %>%
  filter(type == "Latent field") %>%
  select(-type) %>%
  select(Parameter, TMB = `KS(TMB, tmbstan)`, `PCA-AGHQ` = `KS(aghq, tmbstan)`) %>%
  mutate(Difference = `PCA-AGHQ` - TMB) %>%
  gt::gt() %>%
  gt::summary_rows(
   columns = c(`TMB`, `PCA-AGHQ`, Difference),
   fns = list(Average = ~ mean(.x)),
   formatter = gt::fmt_number,
   decimals = 3
  ) %>%
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    decimals = 3
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Difference"),
    fn = function(x) ifelse(x < 0, paste0("\\textbf{", x, "}"), paste0(x))
  ) %>%
  gt::as_latex() %>%
  as.character() %>%
  cat(file = "ks-summary.tex")
```

>>>>

ks_summary %>%
  ungroup() %>%
  filter(type == "Latent") %>%
  select(-type) %>%
  select(Parameter = parname, TMB, `PCA-AGHQ` = aghq) %>%
  mutate(Difference = `PCA-AGHQ` - TMB) %>%
  gt::gt() %>%
  gt::summary_rows(
   columns = c(`TMB`, `PCA-AGHQ`, Difference),
   fns = list(Average = ~ mean(.x)),
   formatter = gt::fmt_number,
   decimals = 3
  ) %>%
  gt::fmt_number(
    columns = c(`TMB`, `PCA-AGHQ`, Difference),
    decimals = 3
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Parameter"),
    fn = function(x) paste0("\\texttt{", x, "}")
  ) %>%
  gt::text_transform(
    locations = gt::cells_body("Difference"),
    fn = function(x) ifelse(x < 0, paste0("\\textbf{", x, "}"), paste0(x))
  ) %>%
  gt::as_latex() %>%
  as.character() %>%
  cat(file = "ks-summary.tex")
```
